---
title: "DM-Project"
author: "Yufei HE"
format: html
editor: visual
---

**A link to the github project:**

https://github.com/hyf19980724/DM-Project.git

**Links to the sources:**

A dataset describing the global warming response to national emissions CO2, CH4 and N2O from fossil and land use sources during 1851-2021. 

[[https://zenodo.org/records/7636699#.ZFCy4exBweZ]{.underline}](#.ZFCy4exBweZ)

Annual consumption-based emissions of CO2 and annual CO2 emissions embedded in trade: 

[[https://www.eia.gov/opendata/index.php#bulk-downloads]{.underline}](#bulk-downloads) ;

[[https://zenodo.org/records/7215364#.Y3y3sezMIeY]{.underline}](#.Y3y3sezMIeY)

Greenhouse gas emissions (including methane and nitrous oxide) by sector :

[https://www.climatewatchdata.org/data-explorer/historical-emissions?historical-emissions-data-sources=climate-watch&historical-emissions-gases=all-ghg&historical-emissions-regions=All%20Selected&historical-emissions-sectors=total-including-lucf%2Ctotal-including-lucf&page=1](https://www.climatewatchdata.org/data-explorer/historical-emissions?historical-emissions-data-sources=climate-watch&historical-emissions-gases=all-ghg&historical-emissions-regions=All Selected&historical-emissions-sectors=total-including-lucf,total-including-lucf&page=1)

Statistical review of world energy:  

[[https://www.energyinst.org/statistical-review]{.underline}](https://www.energyinst.org/statistical-review) ;

[[https://databank.worldbank.org/source/sustainable-development-goals-(sdgs)#]{.underline}](https://databank.worldbank.org/source/sustainable-development-goals-(sdgs))

GDP: 

[[https://www.rug.nl/ggdc/historicaldevelopment/maddison/releases/maddison-project-database-2020]{.underline}](https://www.rug.nl/ggdc/historicaldevelopment/maddison/releases/maddison-project-database-2020)

[[https://databank.worldbank.org/reports.aspx?source=2&series=EN.ATM.CO2E.PC&country=#]{.underline}](https://databank.worldbank.org/reports.aspx?source=2&series=EN.ATM.CO2E.PC&country=)

Population：

[[https://ourworldindata.org/population-sources]{.underline}](https://ourworldindata.org/population-sources)

[[https://en.wikipedia.org/wiki/List_of_countries_and_dependencies_by_population]{.underline}](https://en.wikipedia.org/wiki/List_of_countries_and_dependencies_by_population)

**Description of Sources**

GDP: Gross Domestic Product (GDP) is the core dependent variable representing the economic development level of a country. We sourced GDP data for various countries across different decades from the University of Groningen and the World Bank databases. To maintain consistency, we converted all GDP figures into U.S. dollars, using the U.S. GDP data from 2015 as a benchmark. This approach facilitates cross-country comparisons and temporal analysis.

Population: Population data were acquired from Our World in Data, Wikipedia, and the World Bank. Population is a critical factor influencing both economic development and environmental pollution. Including population in our analysis helps mitigate endogeneity concerns, allowing for a more accurate assessment of the relationships between population dynamics, economic growth, and environmental impacts.

CO2 Metrics: Variables such as \`co2\`, \`co2_per_capita\`, \`co2_per_gdp\`, and \`co2_per_unit_energy\` were sourced from the U.S. Energy Information Administration (EIA) and Zenodo databases. These variables are central explanatory factors representing environmental aspects. We ensured the reliability of these data by cross-verifying between the two databases. Given the varied development levels of countries, total CO2 emissions alone may not fully represent a country's pollution level. Therefore, we included additional variables to assess the heterogeneous impacts of environmental issues on economic growth across different nations.

Methane Metrics: \`methane\` and \`methane_per_capita\` data, similar to CO2 data, were obtained from the same sources. Relying solely on CO2 to indicate environmental pollution has its limitations, as some industries, like the chemical industry, emit other gases like methane. Given that greenhouse gases contributing to global warming are not limited to CO2, incorporating methane data provides a more comprehensive view of environmental pollution.

Energy Consumption Metrics: \`energy_per_capita\` and \`energy_per_gdp\` data were sourced from the Statistical Review of World Energy database and the World Bank. Including energy consumption in our regression analysis is crucial. Energy consumption is not only a direct driver of economic development but also a primary source of environmental pollution. This inclusion helps us explore the causal relationships and conduct channel testing between energy, economy, and environmental pollution.

Climate Change and Trade Variables: \`temperature_change_from_co2\` and \`trade_co2\` data were also sourced from the EIA and Zenodo databases. The increase in temperature due to CO2 emissions significantly impacts economic activities. Moreover, trade activities, being a vital part of the economy---especially in the context of international economic exchanges---can be further analyzed for robustness checks. These variables allow us to understand the broader impacts of environmental change on global trade and economic dynamics.

This expanded and refined data construction provides a solid foundation for analyzing the intricate relationships between economic growth, population dynamics, environmental pollution, and energy consumption. It also allows for a nuanced understanding of how these factors interplay at both the national and global levels.

**Description of each variable:**

**1. Country:** Geographic location.

**2. Year:** Year of observation.

**3. Population:** Population by country and year.

**4. GDP:** Gross domestic product measured in international-\$ using 2011 prices to adjust for price changes over time (inflation) and price differences between countries.

**5. CO2:** Annual total emissions of carbon dioxide (CO2), excluding land-use change, measured in million tonnes.

**6. co2_per_capita:** Annual CO2 emissions (per capita) - Annual total emissions of carbon dioxide (CO2), excluding land-use change, measured in tonnes per person.

**7. co2_per_gdp:** Annual CO2 emissions per GDP (kg per international-\$) - Annual total emissions of carbon dioxide (CO2), excluding land-use change, measured in kilograms per dollar of GDP (2011 international-\$).

**8. co2_per_unit_energy**: Annual CO2 emissions per unit energy (kg per kilowatt-hour) - Annual total emissions of carbon dioxide (CO2), excluding land-use change, measured in kilograms per kilowatt-hour of primary energy consumption.

**9. energy_per_capita:** Primary energy consumption per capita, measured in kilowatt-hours per person per year.

**10. energy_per_gdp:** Primary energy consumption per unit of gross domestic product, measured in kilowatt-hours per international-\$.

**11. Methane:** Total methane emissions including land-use change and forestry - Emissions are measured in million tonnes of carbon dioxide-equivalents.

**12. methane_per_capita:** Total methane emissions per capita including land-use change and forestry - Emissions are measured in tonnes of carbon dioxide-equivalents per person.

**13. temperature_change_from_co2:** Change in global mean surface temperature (in °C) caused by CO2 emissions. This measures each country's contribution to global mean surface temperature (GMST) rise from its cumulative emissions of carbon dioxide. The warming effects of each gas are calculated based on cumulative CO2-equivalent emissions using the Global Warming Potential (GWP\*) approach.

**14. trade_co2:** Annual net carbon dioxide (CO2) emissions embedded in trade, measured in million tonnes.

**Data cleaning:**

In this step, we have cleaned the data by selecting the data from 1991 to 2021 to ensure that the results are not compromised by the age of the data. Additionally, we chose 14 variables for our analysis because these variables are highly relevant to the research question we are investigating. Lastly, we removed missing data, focusing our analysis on countries without missing data. The purpose of data cleaning is to improve data quality, enhance model performance, and increase the efficiency of analysis. It achieves these goals by removing or correcting errors and inconsistencies in the dataset, ensuring that the results of data analysis are more accurate and reliable.

```{r}
#| message: false
here::i_am("DM-Project.Rproj")
library(here)
library(vroom)
library(dplyr)
library(tidyr)
library(ggplot2)
```

```{r}
#| message: false
owid <- vroom(here("owid-co2-data.csv"))
```

```{r}
owid_filtered <- owid %>%
  filter(year >= 1991, year <= 2021)
```

```{r}
owid_selected <- owid_filtered %>%
  select(country, year, population, gdp, co2, co2_per_capita, co2_per_gdp, co2_per_unit_energy, energy_per_capita, energy_per_gdp, methane, methane_per_capita, temperature_change_from_co2, trade_co2)
```

```{r}
owid_selected_no_na <- owid_selected %>%
  filter(
    !is.na(country),
    !is.na(year),
    !is.na(population),
    !is.na(gdp),
    !is.na(co2),
    !is.na(co2_per_capita),
    !is.na(co2_per_gdp),
    !is.na(co2_per_unit_energy),
    !is.na(energy_per_capita),
    !is.na(energy_per_gdp),
    !is.na(methane),
    !is.na(methane_per_capita),
    !is.na(temperature_change_from_co2),
    !is.na(trade_co2)
  )
```

**Tables of basic information about the data file:**

```{r}
dimensions <- dim(owid_selected_no_na)

descriptive_stats <- summary(owid_selected_no_na)

cat("Rows:", dimensions[1], "\n")
cat("Columns:", dimensions[2], "\n\n")
print(descriptive_stats)
```

```{r}
dimensions_2 <- dim(owid)
cat("Rows:", dimensions_2[1], "\n")
cat("Columns:", dimensions_2[2], "\n\n")
```

```{r}
#| message: false
emiss <- vroom(here("EMISSIONS_ANNUAL_1830-2021.csv"))
dimensions_3 <- dim(emiss)
cat("Rows:", dimensions_3[1], "\n")
cat("Columns:", dimensions_3[2], "\n\n")
```
